trying to get line numbers working

### 2017-09-11 inst/documents/paper2/test_linenumbers.Rmd
testing

output: 
  pdf_document:
    #citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
bibliography: library.bib
csl: biomed-central.csl
fontsize: 11pt
spacing: double

@@

Seems that the header-includes bit above does work to add line numbers and double space (although it does generate a few warning messages)

@@

>>>>

# output: 
#   pdf_document:
#     keep_tex: true
#     fig_caption: true
#     latex_engine: pdflatex
output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
bibliography: library.bib
csl: biomed-central.csl
fontsize: 11pt
spacing: double

@@

Seems that the header-includes bit above works to add line numbers and double space to pdf, but not to word doc.

Tables, figs and ref list seem to work both for pdf & word doc.

@@

**Table 2. Effect of inputs on resistance when insecticides used singly or in sequence**

Parameter to increase  | effect on resistance evolution | Mechanism
----------------------- | -------- | ---------------------------------------------
1. Effectiveness | faster | reduced fitness of SS in presence of insecticide
2. Exposure | faster | reduced fitness of SS overall
3. Dominance of restoration | faster | increased fitness of SR in presence of insecticide
4. Resistance restoration | faster | increased fitness of RR in presence of insecticide
5. Frequency  | faster | less change needed to reach resistance threshold
6. Cost of resistance | slower | reduced fitness of RR in absence of insecticide

**Table 3. Effect of inputs on resistance when insecticides used in a mixture**

Parameter to increase  | effect on resistance evolution | Mechanism
----------------------- | ---------- | ---------------------------------------------
1. Effectiveness | **slower** | one insecticide reduces the fitness of individuals resistant to the other thereby reducing selection pressure from the other
2. Exposure | faster (but less than for single) | reduced fitness of individuals susceptible to one insecticide increases selection pressure for that resistance. However at the same time selection pressure is reduced by reduced fitness of resistant individuals caused by the other insecticide
3. Dominance of restoration | faster | increased fitness of heterozygotes
4. Resistance restoration | faster | increased fitness of resistants
5. Frequency  | faster | less change needed to reach resistance threshold
6. Cost of resistance | slower | reduced fitness of resistants in absence of insecticide

\pagebreak

**Table 4. Effect of inputs on the difference between mixture and sequential use**

Parameter to increase  | increase favours mix or sequence | Mechanism
----------------------- | -------- | ---------------------------------------------
1. Effectiveness | mixture | Higher effectiveness gives faster resistance for sequence and slower resistance in mixture
2. Exposure | sequence | Higher exposure gives faster resistance for sequence and mixture but the greater effect on mixture favours sequence.
3. Dominance of restoration | neither | Higher dominance gives faster resistance in both sequences and mixtures such that the difference between them is not changed. 
4. Resistance restoration | neither | As for dominance of restoration. Higher resistance restoration gives faster resistance in both sequences and mixtures such that the difference between them is not changed.
5. Frequency  | neither | As for dominance and resistance restoration. Higher starting frequencies give faster resistance in both sequences and mixtures such that the difference between them is not changed.
6. Cost of resistance | mixture | Higher costs slow the evolution of resistance more in a mixture than when used in sequence (but with higher costs in a sequence there is a greater chance for resistance levels to decline for the insecticide not being used).

### 2017-09-11 inst/documents/paper2/test_linenumbers.tex
testing

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={trying to get line numbers working},
            pdfauthor={Andy South and Ian Hastings},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{trying to get line numbers working}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Andy South and Ian Hastings}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{2017-04-11}

@@

@@

Insecticide resistance is a problem for malaria
\citep{WHO2012}\citep{Ranson2016}\citep{Hemingway2016} other vector
borne diseases \citep{IRAC2011} and agriculture \citep{FAO2012}. Malaria
alone still results in hundreds of thousands of deaths per year. Recent
malaria control efforts have centred on treated bed nets and indoor
residual spraying, both reliant on insecticides. Treated nets were
recently estimated to contribute 68\% and indoor residual spraying 13\%
to averting more than 500 million falciparum malaria cases between 2000
and 2015 \citep{Bhatt2015}. A recent malaria transmission model
\citep{Churcher2016} predicts that even low pyrethroid resistance is
likely to increase malaria incidence in Africa by reducing the
performance of bed nets.

The WHO produced a Global Plan for Insecticide Resistance Management in
malaria vectors (GPIRM)\citep{WHO2012} which includes recommendations on
operational strategies for managing resistance including the use of
insecticide mixtures when they become available. Efforts are under way
to develop new insecticides that will be effective in the light of
existing resistance and allow additional options within insecticide
resistance management. The Innovative Vector Control Consortium (IVCC)
was set up in 2005 to develop new vector control tools and particularly
new insecticides to address insecticide resistance in malaria
transmitting mosquitoes \citep{Hemingway2006}\citep{IVCC2016}. Three new
insecticides are now in development \citep{IVCC2016} and likely to be
available around 2020 \citep{Ranson2016}. It is important that decisions
about how best to use the new insecticides to delay the onset of
resistance are made before insecticides are released
\citep{Hemingway2016}.

Modelling studies have investigated the evolution of insecticide
resistance in insecticide mixtures including in a public health context
e.g. \citep{Curtis1985}\citep{Mani1985}\citep{Roush1989} but much of the
work was done more than 20 years ago and there remained some confusion
about the results \citep{Levick2017}. In an earlier paper
\citep{Levick2017} we described the technical details of a flexible
model used to investigate the relative benefits of mixtures and
sequences. Here we provide an accessible summary of the model and use
selected parameter values to describe mechanistically how the evolution
of resistance is influenced by different inputs. This mechanistic
understanding can contribute to the debate on the relative merits of
different insecticide strategies extending existing frameworks
\citep{Roush1989}\citep{IRAC2011}\citep{FAO2012}\citep{WHO2012}.

@@

\bibliography{library}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={trying to get line numbers working},
            pdfauthor={Andy South and Ian Hastings},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{trying to get line numbers working}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Andy South and Ian Hastings}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{2017-09-11}

@@

Seems that the header-includes bit above does work to add line numbers
and double space (although it does generate a few warning messages)

@@

Insecticide resistance is a problem for malaria {[}1{]}{[}2{]}{[}3{]}
other vector borne diseases {[}4{]} and agriculture {[}5{]}. Malaria
alone still results in hundreds of thousands of deaths per year. Recent
malaria control efforts have centred on treated bed nets and indoor
residual spraying, both reliant on insecticides. Treated nets were
recently estimated to contribute 68\% and indoor residual spraying 13\%
to averting more than 500 million falciparum malaria cases between 2000
and 2015 {[}6{]}. A recent malaria transmission model {[}7{]} predicts
that even low pyrethroid resistance is likely to increase malaria
incidence in Africa by reducing the performance of bed nets.

The WHO produced a Global Plan for Insecticide Resistance Management in
malaria vectors (GPIRM){[}1{]} which includes recommendations on
operational strategies for managing resistance including the use of
insecticide mixtures when they become available. Efforts are under way
to develop new insecticides that will be effective in the light of
existing resistance and allow additional options within insecticide
resistance management. The Innovative Vector Control Consortium (IVCC)
was set up in 2005 to develop new vector control tools and particularly
new insecticides to address insecticide resistance in malaria
transmitting mosquitoes {[}8{]}{[}9{]}. Three new insecticides are now
in development {[}9{]} and likely to be available around 2020 {[}2{]}.
It is important that decisions about how best to use the new
insecticides to delay the onset of resistance are made before
insecticides are released {[}3{]}.

Modelling studies have investigated the evolution of insecticide
resistance in insecticide mixtures including in a public health context
e.g. {[}10{]}{[}11{]}{[}12{]} but much of the work was done more than 20
years ago and there remained some confusion about the results {[}13{]}.
In an earlier paper {[}13{]} we described the technical details of a
flexible model used to investigate the relative benefits of mixtures and
sequences. Here we provide an accessible summary of the model and use
selected parameter values to describe mechanistically how the evolution
of resistance is influenced by different inputs. This mechanistic
understanding can contribute to the debate on the relative merits of
different insecticide strategies extending existing frameworks
{[}12{]}{[}4{]}{[}5{]}{[}1{]}.

@@

\textbf{Table 2. Effect of inputs on resistance when insecticides used
singly or in sequence}

\begin{longtable}[]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.28\columnwidth}\raggedright\strut
Parameter to increase\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
effect on resistance evolution\strut
\end{minipage} & \begin{minipage}[b]{0.53\columnwidth}\raggedright\strut
Mechanism\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
1. Effectiveness\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
reduced fitness of SS in presence of insecticide\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
2. Exposure\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
reduced fitness of SS overall\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
3. Dominance of restoration\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
increased fitness of SR in presence of insecticide\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
4. Resistance restoration\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
increased fitness of RR in presence of insecticide\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
5. Frequency\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
less change needed to reach resistance threshold\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
6. Cost of resistance\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
slower\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
reduced fitness of RR in absence of insecticide\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\textbf{Table 3. Effect of inputs on resistance when insecticides used
in a mixture}

\begin{longtable}[]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.27\columnwidth}\raggedright\strut
Parameter to increase\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
effect on resistance evolution\strut
\end{minipage} & \begin{minipage}[b]{0.52\columnwidth}\raggedright\strut
Mechanism\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
1. Effectiveness\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\textbf{slower}\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
one insecticide reduces the fitness of individuals resistant to the
other thereby reducing selection pressure from the other\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
2. Exposure\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
faster (but less than for single)\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
reduced fitness of individuals susceptible to one insecticide increases
selection pressure for that resistance. However at the same time
selection pressure is reduced by reduced fitness of resistant
individuals caused by the other insecticide\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
3. Dominance of restoration\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
increased fitness of heterozygotes\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
4. Resistance restoration\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
increased fitness of resistants\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
5. Frequency\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
faster\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
less change needed to reach resistance threshold\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
6. Cost of resistance\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
slower\strut
\end{minipage} & \begin{minipage}[t]{0.52\columnwidth}\raggedright\strut
reduced fitness of resistants in absence of insecticide\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\pagebreak

\textbf{Table 4. Effect of inputs on the difference between mixture and
sequential use}

\begin{longtable}[]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.28\columnwidth}\raggedright\strut
Parameter to increase\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
increase favours mix or sequence\strut
\end{minipage} & \begin{minipage}[b]{0.53\columnwidth}\raggedright\strut
Mechanism\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
1. Effectiveness\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
mixture\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
Higher effectiveness gives faster resistance for sequence and slower
resistance in mixture\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
2. Exposure\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
sequence\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
Higher exposure gives faster resistance for sequence and mixture but the
greater effect on mixture favours sequence.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
3. Dominance of restoration\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
neither\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
Higher dominance gives faster resistance in both sequences and mixtures
such that the difference between them is not changed.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
4. Resistance restoration\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
neither\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
As for dominance of restoration. Higher resistance restoration gives
faster resistance in both sequences and mixtures such that the
difference between them is not changed.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
5. Frequency\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
neither\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
As for dominance and resistance restoration. Higher starting frequencies
give faster resistance in both sequences and mixtures such that the
difference between them is not changed.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright\strut
6. Cost of resistance\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
mixture\strut
\end{minipage} & \begin{minipage}[t]{0.53\columnwidth}\raggedright\strut
Higher costs slow the evolution of resistance more in a mixture than
when used in sequence (but with higher costs in a sequence there is a
greater chance for resistance levels to decline for the insecticide not
being used).\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{refs}{}
\hypertarget{ref-WHO2012}{}
1. WHO: \emph{Global plan for insecticide resistance management in
malaria vectors (GPIRM).} Geneva. 2012:130.

\hypertarget{ref-Ranson2016}{}
2. Ranson H, Lissenden N: \textbf{Insecticide Resistance in African
Anopheles Mosquitoes: A Worsening Situation that Needs Urgent Action to
Maintain Malaria Control}. \emph{Trends in Parasitology} 2016,
\textbf{32}:187--196.

\hypertarget{ref-Hemingway2016}{}
3. Hemingway J, Ranson H, Magill A, Kolaczinski J, Fornadel C, Gimnig J,
Coetzee M, Simard F, Roch DK, Hinzoumbe CK, Pickett J, Schellenberg D,
Gething P, Hoppé M, Hamon N: \textbf{Averting a malaria disaster: Will
insecticide resistance derail malaria control?} \emph{The Lancet} 2016,
\textbf{387}:1785--1788.

\hypertarget{ref-IRAC2011}{}
4. IRAC: \emph{Prevention and Management of Insecticide Resistance in
Vectors of Public Health Importance}. 2011:71.

\hypertarget{ref-FAO2012}{}
5. FAO: \emph{Guidelines on Prevention and Management of Pesticide
Resistance}. Rome; 2012:55.

\hypertarget{ref-Bhatt2015}{}
6. Bhatt S, Weiss DJ, Cameron E, Bisanzio D, Mappin B, Dalrymple U,
Battle KE, Moyes CL, Henry A, Eckhoff PA, Wenger EA, Briët O, Penny MA,
Smith TA, Bennett A, Yukich J, Eisele TP, Griffin JT, Fergus CA, Lynch
M, Lindgren F, Cohen JM, Murray CLJ, Smith DL, Hay SI, Cibulskis RE,
Gething PW: \textbf{The effect of malaria control on Plasmodium
falciparum in Africa between 2000 and 2015.} \emph{Nature} 2015,
\textbf{526}:207--11.

\hypertarget{ref-Churcher2016}{}
7. Churcher TS, Lissenden N, Griffin JT, Worrall E, Ranson H:
\textbf{The impact of pyrethroid resistance on the efficacy and
effectiveness of bednets for malaria control in Africa}. \emph{eLife}
2016, \textbf{5}:e16090.

\hypertarget{ref-Hemingway2006}{}
8. Hemingway J, Beaty BJ, Rowland M, Scott TW, Sharp BL: \textbf{The
Innovative Vector Control Consortium: improved control of mosquito-borne
diseases}. \emph{Trends in Parasitology} 2006, \textbf{22}:308--312.

\hypertarget{ref-IVCC2016}{}
9. IVCC: \textbf{Annual Report 2015-16}. 2016.

\hypertarget{ref-Curtis1985}{}
10. Curtis CF: \textbf{Theoretical models of the use of insecticide
mixtures for the management of resistance}. \emph{Bulletin of
Entomological Research} 1985, \textbf{75}:259.

\hypertarget{ref-Mani1985}{}
11. Mani GS: \textbf{Evolution of resistance in the presence of two
insecticides.} \emph{Genetics} 1985, \textbf{109}:761--783.

\hypertarget{ref-Roush1989}{}
12. Roush RT: \textbf{Designing resistance management programs: How can
you choose?} \emph{Pesticide Science} 1989, \textbf{26}:423--441.

\hypertarget{ref-Levick2017}{}
13. Levick B, South A, Hastings IM: \textbf{A Two-locus Model of The
Evolution of Insecticide Resistance to Inform and Optimise Public Health
Insecticide Deployment Strategies.} \emph{PLOS Computational Biology}
2017.
